Data Exploration: IUCN and AquaMaps

### 2016-09-23 clip_depth/coral_maps.Rmd
wrapping up edits from JA, BH, CS updating fig captions

bath_df <-  read_csv(file.path(dir_git, 'clip_depth', 'bathy_cells.csv'), col_types = 'dd') %>%
  filter(weight >= 1) %>% ### cell must be 100% within the deep polygon to count as deep
  mutate(deep = 1) %>%
  select(-weight)

@@

### load iucn spp_cells
coral_files <- list.files(file.path(dir_anx, 'v2016', 'iucn_intersections'), 
                          pattern = 'CORAL*.*',
                          full.names = TRUE)
coral_cells_iucn <- lapply(coral_files, read_csv) %>%
  bind_rows() %>%
  select(iucn_sid, loiczid = LOICZID) %>%
  # filter(iucn_sid %in% spp_depth$iucn_sid[spp_depth$paired_map]) %>%
  left_join(bath_df, by = 'loiczid') %>%
  mutate(deep = ifelse(is.na(deep), 0, deep))

@@

  spp_depth <- spp_narr %>%
    select(iucn_sid = species_id, habitat) %>%
    mutate(paired_map = (iucn_sid %in% spp_map_pairs$iucn_sid))

@@

rast_coral_comp <- raster::subs(x = loiczid_raster, y = coral_comp %>% select(loiczid, deep), 
                     by = 'loiczid', which = 'deep', 
                     subsWithNA = TRUE) %>%
  crop(extent(c(-180, 180, -63, 85)))

@@

hcaf <- read_csv(file.path(dir_anx, '../_raw_data/aquamaps/d2015/csv/hcaf_truncated.csv')) %>%
  select(loiczid, cellarea, oceanarea)

@@

  spp_coralmaps <- read_csv(file.path(dir_data, 'spp_list_w_area_trimmed.csv')) %>%
    filter(iucn_sid %in% coral_cells_iucn_shallow$iucn_sid) %>%
    select(am_sid, sciname, iucn_sid)

@@

  for (sid in sid_vector) { 
    # sid <- spp_coralmaps$iucn_sid[1]
    i <- i + 1
    sids <- spp_coralmaps %>% 
      select(am_sid, iucn_sid, sciname) %>%
      filter(iucn_sid == sid)
    rowindex <- (spp_coralmaps$iucn_sid == sid)

@@

    r_am_spp <- subs(x = loiczid_raster, y = map_am %>% select(loiczid, am_pres), 
                     by = 'loiczid', which = 'am_pres', 
                     subsWithNA = TRUE)

    ### rasterize IUCN map
    if(TRUE %in% duplicated(map_iucn$loiczid)) stop('Duplicated cells in IUCN map')
    r_iucn_spp <- subs(loiczid_raster, map_iucn %>% select(loiczid, iucn_pres), 
                       by = 'loiczid', which = 'iucn_pres', 
                       subsWithNA = TRUE)

@@

  spp_coralmaps <- spp_coralmaps %>%
    mutate(lg_area = ifelse(area_am > area_iucn, area_am, area_iucn),
           sm_area = ifelse(area_am < area_iucn, area_am, area_iucn),
           lg_area_pct = 100 * lg_area / max(area_total, na.rm = TRUE)) %>% 
             ### use largest data set as approx for total ocean range
    select(-lg_area, -sm_area)

@@

  ### combine old and new area dataframes
  spp_coralmaps <- spp_coralmaps %>%
    select(iucn_sid, am_sid, sciname, area_am, 
           area_iucn_shallow = area_iucn, area_overlap_shallow = area_overlap, 
           sm_perc_shallow = sm_perc, sm_range_shallow = sm_range, area_ratio_shallow = area_ratio) %>%
    left_join(read_csv(file.path(dir_data, 'spp_list_w_area_trimmed.csv')) %>%
                select(am_sid, iucn_sid, 
                       area_iucn_raw = area_iucn, area_overlap_raw = area_overlap, 
                       sm_perc_raw = sm_perc, sm_range_raw = sm_range, area_ratio_raw = area_ratio),
              by = c('iucn_sid', 'am_sid'))

@@

spp_coral_clip <- read_csv(file.path(dir_git, 'clip_depth', 'iucn_coral_areas.csv')) %>%
  select(iucn_sid, shallow_pct, deep_pct, totarea, shallow_area = area) %>%
  mutate(shallow_pct = 100 * shallow_pct,
         deep_pct    = 100 * deep_pct)

@@

iucn_coral_quads <- iucn_coral_fixed %>%
  select(iucn_sid, sciname, d_perc, a_ratio, method) %>% ### ditch am_sid, b/c duplicates
  distinct() %>%
  mutate(quad = 'q1',
         quad = ifelse(a_ratio < area_align_mean  & d_perc >= dist_align_mean, 'q2', quad),
         quad = ifelse(a_ratio >= area_align_mean & d_perc < dist_align_mean,  'q3', quad),
         quad = ifelse(a_ratio < area_align_mean  & d_perc < dist_align_mean,  'q4', quad)) %>%
  group_by(method) %>%
  mutate(n_total = n()) %>%
  group_by(method, quad) %>%
  mutate(n_quad = n(),
         pct_quad = n_quad/n_total) %>%
  ungroup()

quad_names <- data.frame('quad' = c('q1', 'q2', 'q3', 'q4'),
                         'quad_name' = factor(c('well-matched', 'dist-matched', 
                                                'area-matched', 'poorly matched'),
                                             ordered = TRUE))

@@

iucn_coral_quad_sum <- read_csv(file.path(dir_git, 'clip_depth', 'iucn_coral_quads.csv')) %>%
  select(method, quad, quad_name, pct_quad) %>%
  distinct()
### Plot the bar chart
barchart_coral_quads <- ggplot(iucn_coral_quad_sum, 
                                aes(x = method, fill = quad, weight = pct_quad)) +
  ggtheme_plot + 
  theme(panel.grid.major.y = element_blank()) +
  geom_bar(stat = 'count', alpha = 1) +
  scale_fill_manual(values = c('q4' = '#d01c8b', 
                               'q3' = '#f1b6da', 
                               'q2' = '#b8e186',
                               'q1' = '#4dac26'),
                    labels = quad_names$quad_name) +
  scale_y_continuous(expand = c(0, 0), 
                     limits = c(0, 1),
                     breaks = break_nums/100,
                     labels = sprintf('%s%%', break_nums)) + 
  ### add grid lines; horizontal but then get flipped
  geom_hline(yintercept = break_nums/100, size = 0.25, color = 'white', alpha = .5) +
  coord_flip() +
  labs(x = 'Taxonomic Group', 
       y = 'Percent of corals by quadrant', 
       fill = 'Alignment')

@@

ggsave(plot = barchart_coral_quads,
       filename = file.path(dir_fig, 'barchart_coral_quads.png'),
       width = 19, height = 4, units = 'cm', dpi = 600)

>>>>

bath_df <-  read_csv(file.path(dir_git, 'clip_depth', 'bathy_cells.csv'), col_types = 'dd') %>%
  filter(weight >= 1) %>% ### cell must be 100% within the deep polygon to count as deep
  mutate(deep = 1) %>%
  dplyr::select(-weight)

@@

### load iucn spp_cells
coral_files <- list.files(file.path(dir_anx, 'v2016', 'iucn_intersections'), 
                          pattern = 'CORAL*.*',
                          full.names = TRUE)
coral_cells_iucn <- lapply(coral_files, read_csv) %>%
  bind_rows() %>%
  dplyr::select(iucn_sid, loiczid = LOICZID) %>%
  # filter(iucn_sid %in% spp_depth$iucn_sid[spp_depth$paired_map]) %>%
  left_join(bath_df, by = 'loiczid') %>%
  mutate(deep = ifelse(is.na(deep), 0, deep))

@@

  spp_depth <- spp_narr %>%
    dplyr::select(iucn_sid = species_id, habitat) %>%
    mutate(paired_map = (iucn_sid %in% spp_map_pairs$iucn_sid))

@@

rast_coral_comp <- raster::subs(x = loiczid_raster, y = coral_comp %>% dplyr::select(loiczid, deep), 
                     by = 'loiczid', which = 'deep', 
                     subsWithNA = TRUE) %>%
  crop(extent(c(-180, 180, -63, 85)))

@@

hcaf <- read_csv(file.path(dir_anx, '../_raw_data/aquamaps/d2015/csv/hcaf_truncated.csv')) %>%
  dplyr::select(loiczid, cellarea, oceanarea)

@@

  spp_coralmaps <- read_csv(file.path(dir_data, 'spp_list_w_area_trimmed.csv')) %>%
    filter(iucn_sid %in% coral_cells_iucn_shallow$iucn_sid) %>%
    dplyr::select(am_sid, sciname, iucn_sid)

@@

  for (sid in sid_vector) { 
    # sid <- spp_coralmaps$iucn_sid[1]
    i <- i + 1
    sids <- spp_coralmaps %>% 
      dplyr::select(am_sid, iucn_sid, sciname) %>%
      filter(iucn_sid == sid)
    rowindex <- (spp_coralmaps$iucn_sid == sid)

@@

    r_am_spp <- subs(x = loiczid_raster, y = map_am %>% dplyr::select(loiczid, am_pres), 
                     by = 'loiczid', which = 'am_pres', 
                     subsWithNA = TRUE)

    ### rasterize IUCN map
    if(TRUE %in% duplicated(map_iucn$loiczid)) stop('Duplicated cells in IUCN map')
    r_iucn_spp <- subs(loiczid_raster, map_iucn %>% dplyr::select(loiczid, iucn_pres), 
                       by = 'loiczid', which = 'iucn_pres', 
                       subsWithNA = TRUE)

@@

  spp_coralmaps <- spp_coralmaps %>%
    mutate(lg_area = ifelse(area_am > area_iucn, area_am, area_iucn),
           sm_area = ifelse(area_am < area_iucn, area_am, area_iucn),
           lg_area_pct = 100 * lg_area / max(area_total, na.rm = TRUE)) %>% 
             ### use largest data set as approx for total ocean range
    dplyr::select(-lg_area, -sm_area)

@@

  ### combine old and new area dataframes
  spp_coralmaps <- spp_coralmaps %>%
    dplyr::select(iucn_sid, am_sid, sciname, area_am, 
           area_iucn_shallow = area_iucn, area_overlap_shallow = area_overlap, 
           sm_perc_shallow = sm_perc, sm_range_shallow = sm_range, area_ratio_shallow = area_ratio) %>%
    left_join(read_csv(file.path(dir_data, 'spp_list_w_area_trimmed.csv')) %>%
                dplyr::select(am_sid, iucn_sid, 
                       area_iucn_raw = area_iucn, area_overlap_raw = area_overlap, 
                       sm_perc_raw = sm_perc, sm_range_raw = sm_range, area_ratio_raw = area_ratio),
              by = c('iucn_sid', 'am_sid'))

@@

spp_coral_clip <- read_csv(file.path(dir_git, 'clip_depth', 'iucn_coral_areas.csv')) %>%
  dplyr::select(iucn_sid, shallow_pct, deep_pct, totarea, shallow_area = area) %>%
  mutate(shallow_pct = 100 * shallow_pct,
         deep_pct    = 100 * deep_pct)

@@

iucn_coral_quads <- iucn_coral_fixed %>%
  dplyr::select(iucn_sid, sciname, d_perc, a_ratio, method) %>% ### ditch am_sid, b/c duplicates
  distinct() %>%
  mutate(quad = 'q1',
         quad = ifelse(a_ratio < area_align_mean  & d_perc >= dist_align_mean, 'q2', quad),
         quad = ifelse(a_ratio >= area_align_mean & d_perc < dist_align_mean,  'q3', quad),
         quad = ifelse(a_ratio < area_align_mean  & d_perc < dist_align_mean,  'q4', quad)) %>%
  group_by(method) %>%
  mutate(n_total = n()) %>%
  group_by(method, quad) %>%
  mutate(n_quad = n(),
         pct_quad = n_quad/n_total) %>%
  ungroup()

quad_names <- data.frame('quad' = c('q1', 'q2', 'q3', 'q4'),
                         'quad_name' = factor(c('well-aligned', 'dist-aligned', 
                                                'area-aligned', 'poorly aligned'),
                                             ordered = TRUE))

@@

iucn_coral_quad_sum <- read_csv(file.path(dir_git, 'clip_depth', 'iucn_coral_quads.csv')) %>%
  dplyr::select(method, quad, quad_name, pct_quad) %>%
  distinct()
### Plot the bar chart
barchart_coral_quads <- ggplot(iucn_coral_quad_sum, 
                                aes(x = method, fill = quad, weight = pct_quad)) +
  ggtheme_plot + 
  theme(panel.grid.major.y = element_blank()) +
  geom_bar(stat = 'count', alpha = 1) +
  scale_fill_manual(values = c('q4' = '#d01c8b', 
                               'q3' = '#f1b6da', 
                               'q2' = '#b8e186',
                               'q1' = '#4dac26'),
                    labels = quad_names$quad_name) +
  scale_y_continuous(expand = c(0, 0), 
                     limits = c(0, 1),
                     breaks = break_nums/100,
                     labels = sprintf('%s%%', break_nums)) + 
  ### add grid lines; horizontal but then get flipped
  geom_hline(yintercept = break_nums/100, size = 0.25, color = 'white', alpha = .5) +
  coord_flip() +
  labs(x = 'Depth limit', 
       y = 'Percent of corals by quadrant', 
       fill = 'Alignment')

@@

# ggsave(plot = barchart_coral_quads,
#        filename = file.path(dir_fig, 'barchart_coral_quads.png'),
#        width = 19, height = 4, units = 'cm', dpi = 600)

### 2016-09-23 clip_fao/fao_clip_pac.Rmd
wrapping up edits from JA, BH, CS updating fig captions

### get quadrant species list; filter to q3 and q4
spp_quad_list <- read_csv(file.path(dir_git, 'data', 'spp_list_quads.csv')) %>%
  select(sciname, am_sid, iucn_sid, reviewed, occurcells, quad) %>%
  filter(quad %in% c('q3', 'q4'))

@@

am_spp_list <- read_csv(file.path(dir_git, 'data/spp_all.csv')) %>%
  filter(!is.na(am_sid)) %>%
  arrange(reviewed) %>%
  filter(!duplicated(am_sid)) %>%
  select(am_sid, sciname, reviewed) %>%
  distinct()

message('loading hcaf and adjusting to se asia')
### join with hcaf to get longitudes (and latitudes) for each cell
hcaf <- read_csv(file.path(dir_anx, '_raw_data/aquamaps/d2015',
                           'csv/hcaf_truncated.csv')) %>%
  select(-csquarecode, -cellarea, -oceanarea) %>%
  mutate(clongadj  = ifelse(centerlong < 0, centerlong + 360, centerlong),
         wlimitadj = ifelse(wlimit < 0, wlimit + 360, wlimit),
         elimitadj = ifelse(elimit < 0, elimit + 360, elimit))

@@

``` {r atlantic_spp} 
### identify species that appear in the mid-atlantic - focus just on pacific/indopacific spp only

@@

message('gathering...')
am_spp_central_lims <- am_spp_central_lims %>%
  gather(lim, long, w_lim:e_lim) %>%
  gather(lim_n, ncells, n_w_lim:n_e_lim) %>%
  filter(str_detect(lim_n, lim)) %>%
  select(-lim_n) %>%
  filter(!(long <= 70 | long >= 200))
    ### delete artificially imposed limits

@@

``` {r what_species_are_these}
### here, the `filter(!am_sid %in% spp_atl)` line eliminates species with a border
### on 185E who also appear in the Atlantic... global species have no eastern/
### western border...
clipped_spp <- am_spp_central_lims %>%
  filter(!am_sid %in% spp_atl) %>%
  filter(long == 185) %>%
  select(am_sid, lim) %>%
  distinct() %>%
  left_join(am_spp_list, by = 'am_sid')

@@

rast_ext  <- extent(c(-30, 330, -75, 75))
fao_polys <- crop(fao_polys, rast_ext)

@@

save_tmap(rast_spp_map_w, 
          file.path(dir_fig, 'map_am_edge_w.png'), 
          width = 19, 
          units = 'cm', dpi = 600)

@@

stack_plot_both <- 
  tm_shape(rast_spp_w) +
    tm_raster(palette = 'Greens',
              colorNA = NULL,
              title = 'n_spp',
              alpha = 1) +
  tm_shape(rast_spp_e) +
    tm_raster(palette = 'Reds',
              colorNA = NULL,
              title = 'n_spp') +
  tm_shape(World1) +
    tm_polygons() + 
  tm_shape(fao_polys) +
    tm_borders() +
  tm_layout(basemaps = "Esri.WorldTopoMap", 
            frame = FALSE,
            # title.position = 'TOP', 
            legend.outside = TRUE, attr.outside = TRUE)

>>>>

### get quadrant species list; filter to q3 and q4
spp_quad_list <- read_csv(file.path(dir_git, 'data', 'spp_list_quads.csv')) %>%
  dplyr::select(sciname, am_sid, iucn_sid, reviewed, occurcells, quad) %>%
  filter(quad %in% c('q3', 'q4'))

@@

am_spp_list <- read_csv(file.path(dir_git, 'data/spp_all.csv')) %>%
  filter(!is.na(am_sid)) %>%
  arrange(reviewed) %>%
  filter(!duplicated(am_sid)) %>%
  dplyr::select(am_sid, sciname, reviewed) %>%
  distinct()

message('loading hcaf and adjusting to se asia')
### join with hcaf to get longitudes (and latitudes) for each cell
hcaf <- read_csv(file.path(dir_anx, '_raw_data/aquamaps/d2015',
                           'csv/hcaf_truncated.csv')) %>%
  dplyr::select(-csquarecode, -cellarea, -oceanarea) %>%
  mutate(clongadj  = ifelse(centerlong < 0, centerlong + 360, centerlong),
         wlimitadj = ifelse(wlimit < 0, wlimit + 360, wlimit),
         elimitadj = ifelse(elimit < 0, elimit + 360, elimit))

@@

``` {r atlantic_spp} 
### identify (to cut) species that appear in the mid-atlantic - focus just on pacific/indopacific spp only

@@

message('gathering...')
am_spp_central_lims <- am_spp_central_lims %>%
  gather(lim, long, w_lim:e_lim) %>%
  gather(lim_n, ncells, n_w_lim:n_e_lim) %>%
  filter(str_detect(lim_n, lim)) %>%
  dplyr::select(-lim_n) %>%
  filter(!(long <= 70 | long >= 200))
    ### delete artificially imposed limits

@@

``` {r what_species_are_these}
### here, the `filter(!am_sid %in% spp_atl)` line eliminates species with a border
### on 185E who also appear in the Atlantic... global species have no eastern/
### western border...
clipped_spp <- am_spp_central_lims %>%
  filter(!am_sid %in% spp_atl) %>%
  filter(long == 185) %>%
  dplyr::select(am_sid, lim) %>%
  distinct() %>%
  left_join(am_spp_list, by = 'am_sid')

@@

rast_ext  <- extent(c(-30, 330, -63, 75)) ### was -75 but changed to -63 to cut more from bottom
fao_polys <- crop(fao_polys, rast_ext)

@@

# save_tmap(rast_spp_map_w, 
#           file.path(dir_fig, 'map_am_edge_w.png'), 
#           width = 19, 
#           units = 'cm', dpi = 600)

``` {r plot_several_spp_w, echo = FALSE, warning = FALSE, message = FALSE, eval = TRUE}

spp_w_cells <- am_spp_cells %>%
  filter(am_sid %in% spp_examples_w$am_sid)

spp_w_all <- spp_w_cells %>%
  group_by(am_sid) %>%
  summarize(n_cells = n())

spp_w_samples <- spp_w_all %>%
  filter(n_cells > 9000) %>% ### focus on large-range species
  sample_n(20) %>%
  .$am_sid

print(spp_w_all %>% filter(am_sid %in% spp_w_samples))
### some good candidates:
#     am_sid n_cells
# Fis-143854   23422
#  Fis-34036   13796
# URM-2-3539   16664
#  Fis-33989   15715
spp_plotted <- read_csv('data/spp_all.csv') %>%
  filter(am_sid %in% spp_w_samples) %>%
  left_join(read_csv('data/speciesoccursum.csv') %>%
              dplyr::select(am_sid = speciesid, occurcells, fbname),
            by = 'am_sid')

for(spp in spp_w_samples) {
  # spp <- spp_w_samples[1]
  message('Processing map for ', spp)
  message('... filtering cells for ', spp)
  spp_cells <- spp_w_cells %>%
    filter(am_sid == spp) %>%
    mutate(presence = 1)
  rast_spp  <-  subs(loiczid_raster, 
                     spp_cells[ , c('loiczid', 'presence')], 
                     by = 'loiczid', 
                     which = 'presence', 
                     subsWithNA = TRUE)

  message('... shifting raster and setting 0 to NA for ', spp)
  rast_spp_shift <- rast_spp %>%
    raster::shift(360)

  message('... generating map for ', spp)

  rast_spp_map_w <- 
    tm_shape(rast_spp_w) +
      tm_raster(palette = 'Reds',
                colorNA = '#ddeeff',
                textNA = 'not present',
                title = spp,
                alpha = 1) +
    tm_shape(World1) +
      tm_polygons(border.col = 'grey45', col = 'grey40', lwd = 0.25) + 
    tm_shape(fao_polys) +
      tm_borders(col = 'grey40', lwd = 0.25) +
      tm_text('F_AREA_1',
              col = 'royalblue4',
              fontface = 'bold.italic',
              fontfamily = 'Helvetica',
              size = .5) +
    tm_shape(fao_boundary) +
      tm_lines(col = 'blue', lwd = 1.5) +
    tm_layout(# basemaps = "Esri.WorldTopoMap", 
              frame = TRUE,
              legend.text.size = .6,
              legend.title.size = .7,
              # title.position = 'TOP', 
              legend.outside = FALSE,
              legend.position = c('right', 'top'),
              legend.bg.color = 'white',
              legend.bg.alpha = .95,
              attr.outside = TRUE)

  print(rast_spp_map_w)
}

# save_tmap(rast_spp_map_w, 
#           file.path(dir_fig, 'map_am_edge_w.png'), 
#           width = 19, 
#           units = 'cm', dpi = 600)

``` {r plot_selected_spp, echo = FALSE, warning = FALSE, message = FALSE, eval = TRUE}

### Select four example species
spp_ex <- c('Hoplichthys regani' = 'Fis-34036', 
            'Ipnops meadi'       = 'Fis-143854', 
            'Culeolus herdmani'  = 'URM-2-3539', 
            'Chrionema chlorotaenia' = 'Fis-33989')

spp_ex_cells <- am_spp_cells %>%
  filter(am_sid %in% spp_ex)

spp_ex_info <- read_csv('data/spp_all.csv') %>%
  filter(am_sid %in% spp_ex)

for(i in 1:length(spp_ex)) {
  # i <- 1
  spp <- spp_ex[i]
  spp_name <- names(spp_ex)[i]

  message('Processing map for ', spp)

  message('... loading occurrences for ', spp)
  spp_occur <- read_csv(paste0('clip_fao/obs_for_', tolower(spp) %>% 
                                 str_replace_all('-', '_'), '.csv')) %>%
    mutate(long = ifelse(long < 0, long + 360, long),
           obs = toupper(obs),
           obs = ifelse(obs == 'BOTH', 'Both', obs),
           obs = factor(obs, levels = c('OBIS', 'GBIF', 'Both')))
  spp_occur_pts <- SpatialPointsDataFrame(spp_occur[ , 1:2], data = spp_occur[ , 3])

  message('... creating raster for ', spp)
  spp_cells <- spp_ex_cells %>%
    filter(am_sid == spp) %>%
    mutate(presence = 1)
  rast_spp  <-  subs(loiczid_raster, 
                     spp_cells[ , c('loiczid', 'presence')], 
                     by = 'loiczid', 
                     which = 'presence', 
                     subsWithNA = TRUE)

  message('... shifting raster and setting 0 to NA for ', spp)
  rast_spp_shift <- rast_spp %>%
    raster::shift(360)

  rast_spp <- merge(rast_spp, rast_spp_shift)

  values(rast_spp)[values(rast_spp) == 0] <- NA
  rast_spp  <- crop(rast_spp, rast_ext)

  message('... generating map for ', spp)

  rast_spp_map <- 
    tm_shape(rast_spp) +
      tm_raster(palette = 'Reds',
                colorNA = '#ddeeff',
                textNA  = 'not present',
                # title   = spp_name,
                legend.show = FALSE,
                showNA  = FALSE,
                alpha   = 1) +
    tm_shape(World1) +
      tm_polygons(border.col = 'grey45', col = 'grey40', lwd = 0.25) + 
    tm_shape(fao_polys) +
      tm_borders(col = 'grey40', lwd = 0.25) +
      tm_text('F_AREA_1',
              col = 'royalblue4',
              fontface = 'bold.italic',
              fontfamily = 'Helvetica',
              size = .5) +
    tm_shape(fao_boundary) +
      tm_lines(col = 'blue', lwd = 1.5)

  rast_map <- rast_spp_map +
    tm_shape(spp_occur_pts) + 
      tm_bubbles(col = 'obs',
                 title.col = 'Occurrences ',
                 palette = c('red', 'blue', 'green'),
                 border.col = 'red',
                 border.lwd = 0.25,
                 border.alpha = 1,
                 size = 1,
                 scale = .3,
                 alpha = .3) +
      # tm_dots(col = 'red') +
    tm_layout(# title = spp_name,
              title.position = c('left', 'bottom'),
              fontface = 'bold.italic',
              fontfamily = 'Helvetica',
              title.size = .8,
              frame = TRUE,
              legend.text.size = .6,
              legend.title.size = .7,
              legend.outside = FALSE,
              legend.position = c('right', 'top'),
              legend.bg.color = 'white',
              legend.bg.alpha = .95,
              attr.outside = TRUE)

  print(rast_map)

  message('... saving map')
  save_tmap(rast_map,
            paste0('clip_fao/map_fao_clip_', tolower(spp_name) %>% 
                     str_replace_all(' ', '_'), '.png'),
            width = 19,
            units = 'cm', dpi = 600)

}

# save_tmap(rast_spp_map_w, 
#           file.path(dir_fig, 'map_am_edge_w.png'), 
#           width = 19, 
#           units = 'cm', dpi = 600)

``` {r quad_spp_w, echo = FALSE, warning = FALSE, message = FALSE, eval = TRUE}

am_spp_cells <- read_csv(file.path(dir_anx, 'spp_ico',
                                   'v2016/int/am_cells_spp_prob0.csv'))

am_spp_list <- read_csv(file.path(dir_anx, '_raw_data/aquamaps/d2015/csv/speciesoccursum.csv')) %>%
  dplyr::select(am_sid = speciesid, genus, species, reviewed, occurcells) %>%
  mutate(sciname = paste(str_trim(genus), str_trim(species), sep = ' ')) %>%
  dplyr::select(-genus, -species) %>%
  distinct()

hcaf <- read_csv(file.path(dir_anx, '_raw_data/aquamaps/d2015/csv/hcaf_truncated.csv')) %>%
  dplyr::select(loiczid, cellarea, oceanarea)

am_spp_cells2 <- hcaf %>%
  left_join(am_spp_cells, by = 'loiczid')

clipped_spp <- read_csv(file.path(dir_git, 'clip_fao', 'clipped_mid_pac.csv')) %>%
  filter(lim == 'e_lim') %>%
  dplyr::select(am_sid)

spp_quad_list <- read_csv(file.path(dir_data, 'spp_list_quads.csv'))

spp_area_df <- am_spp_cells2 %>%
  group_by(am_sid) %>%
  summarize(cellarea = sum(cellarea),
            oceanarea = sum(oceanarea))

spp_area_df <- spp_area_df %>%
  inner_join(am_spp_list, by = 'am_sid') %>%
  mutate(area_per_cells = oceanarea/occurcells)

head(spp_area_df)
#                                     am_sid    cellarea   oceanarea reviewed occurcells                   sciname
#                                      <chr>       <dbl>       <dbl>    <chr>      <int>                     <chr>
# 1                                Biv-32126   949988.02   642706.64     null          4        Corbicula japonica
# 2                                Biv-32832  9698932.54  7589672.98     null         23          Polymesoda erosa
# 3                               Bra-235673    16143.75    13895.96        1         10       Dyscritosia secreta
# 4 Chn-013ca97e-46a8-4c5e-b398-8bb4f340f88b 11288439.81 10048833.94     null         76          Lenisquilla lata
# 5 Chn-015453c0-3ff9-477d-ab51-c68d85e65af5 15078672.39 12760166.60     null         13        Clorida albolitura
# 6 Chn-0721ac0c-7d19-46fa-9dcc-02da54310867 35256268.05 33846838.22     null         23 Leiogalathea laevirostris
summary(spp_area_df$oceanarea)
   # Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
   # 1806    946600   2921000  10210000   7875000 501300000 
summary(spp_area_df$occurcells)
   # Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
   # 0.00    6.00   16.00   57.13   49.00 7663.00 
summary(spp_area_df %>% filter(occurcells != 0) %>% .$area_per_cells)
    # Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
    #  190    50540   158000   485300   439100 44700000 
nrow(spp_area_df %>% filter(!str_detect(reviewed, 'null')))
   # 1296 out of 22889 = 5.66%

spp_area_clipped <- spp_area_df %>%
  filter(am_sid %in% clipped_spp$am_sid)
nrow(spp_area_clipped %>% filter(!str_detect(reviewed, 'null')))
   # 22 out of 3208 = .686%

summary(spp_area_clipped$oceanarea)
   #   Min.   1st Qu.    Median      Mean   3rd Qu.      Max. 
   # 134900   4646000   7032000   8960000   9690000 111300000 
summary(spp_area_clipped$occurcells)
   # Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
   # 3.00    6.00   15.00   26.86   33.00  494.00 
summary(spp_area_clipped$area_per_cells)
    # Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
    # 6578   202900   452400   827200   923300 26090000

# quad_names <- data.frame('quad' = c('q1', 'q2', 'q3', 'q4'),
#                          'quad_name' = factor(c('well-matched', 'dist-matched', 
#                                                 'area-matched', 'poorly matched'),
#                                              ordered = TRUE))
# 
# clipped_spp_quads <- clipped_spp_quads %>%
#   left_join(quad_names, by = 'quad') %>%
#   mutate(method = 'FAO clipped')
# 
# break_nums <- seq(0, 100, 20)

### Plot the bar chart
# barchart_clipped_spp_quads <- ggplot(clipped_spp_quads, 
#                                 aes(x = method, fill = quad, weight = pct_quad)) +
#   ggtheme_plot + 
#   theme(panel.grid.major.y = element_blank()) +
#   geom_bar(stat = 'count', alpha = 1) +
#   scale_fill_manual(values = c('q4' = '#d01c8b', 
#                                'q3' = '#f1b6da', 
#                                'q2' = '#b8e186',
#                                'q1' = '#4dac26'),
#                     labels = quad_names$quad_name) +
#   scale_y_continuous(expand = c(0, 0), 
#                      limits = c(0, 1),
#                      breaks = break_nums/100,
#                      labels = sprintf('%s%%', break_nums)) + 
#   ### add grid lines; horizontal but then get flipped
#   geom_hline(yintercept = break_nums/100, size = 0.25, color = 'white', alpha = .5) +
#   coord_flip() +
#   labs(x = '', 
#        y = 'Percent of species by quadrant', 
#        fill = 'Alignment')
# 
# print(barchart_clipped_spp_quads)

@@

stack_plot_both <- 
  tm_shape(rast_spp_w) +
    tm_raster(palette = 'Greens',
              colorNA = NULL,
              title = 'n_spp',
              alpha = 1) +
  tm_shape(rast_spp_e) +
    tm_raster(palette = 'Reds',
              colorNA = NULL,
              title = 'n_spp') +
  tm_shape(World1) +
    tm_polygons() + 
  tm_shape(fao_polys) +
    tm_borders() +
  tm_layout(basemaps = "Esri.WorldTopoMap", 
            frame = TRUE,
            # title.position = 'TOP', 
            legend.outside = TRUE, attr.outside = TRUE)
